### 2023-09-03 sections/2-methods.tex
new geometry caption

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{images/geometry/geometry.pdf}
    \caption{Scaling Behavior of Radii in a Two-Dimensional Uniform-Density Disk. $R$ 
    denotes the radius of the root cluster $C$, and $o$ denotes its center. The right 
    triangle formed by $o$, $o'$, and $y+$ in $C'$ shows that $R \leq R'$, where $R'$ is the radius of $C'$.
    Hence, the radius of a child cluster can be larger than its parent. $C''$ 
    illustrates that after we have consumed all $d$ axes, the radius of a child cluster
    is bounded above by $\frac{R}{\sqrt{2}}$.}
    \label{fig:methods:scaling_behavior}
\end{figure}

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{images/geometry/geometry.pdf}
    \caption{Scaling behavior of radii in the worst case two-dimensional scenario, 
    a uniform-density disk. $R_0$ denotes the radius of the root cluster $C_0$, and $o_0$ denotes its center. 
    After one application of Algorithm~\ref{1}, we have $C_1$, with radius $R_1$ and center $o_1$.
    The right triangle formed by $o_0$, $o_1$, and $y_+$ in $C_1$ shows that $R_0 \leq R_1$.
    Hence, the radius of a child cluster can be larger than its parent. However, 
    after another application of Algorithm~\ref{1}, we have consumed all $d$ orthogonal axes, 
    as shown in $C_2$. Now, clearly $R_2 \leq R_0$. In fact, for each subsequent application of Algorithm~\ref{1},
    the radius of the resulting cluster is bounded above by $\frac{\sqrt{2}R}{2}$.}
    \label{fig:methods:scaling_behavior}
\end{figure}
